---
title: "Analyses lung cancer datasets"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

## Analyses performed

The analyses performed in this pipeline are:

- Data processing

- Analysis of patients' characteristics

- Survival analysis

### Data processing

In this step, we adjusted some varaibles that did not have the correct format to start the analyses.
In particular, we adjused `age` and `sex` variables:

- `age`: missing values were indicated as `-`; these were transformed into `NA` values

- `sex`: the sex was indicated both with character values (`Male`, `Female`) and with numeric values (`1`,`2`), the latter were transformed into character values (`1 = Male`, `2 = Female`).

### Analysis of patients' characteristics

Here, we calculated patients' statistics for each given variable.
The results are reported below:

```{r, out.width = "100%", out.height="300px"}
list_patients_info_files <- snakemake@input[['patients_info']]
knitr::include_graphics(normalizePath(list_patients_info_files), error=F)
```

### Survival analysis

Here, we performed survival analysis without stratification and with data stratified by `sex`.
The results are reported below:

```{r, out.width = "100%", out.height="400px"}
list_surv_analysis_files <- snakemake@input[['surv_analysis']]
knitr::include_graphics(normalizePath(list_surv_analysis_files), error=F)
```